\PaperTitle

### 2024-05-02 Final_Report/paper.tex
Added in subsubsections to section 2
Touch ups

\subsection{Capturing Data}
\subsection{Data Preparation and Processing}
\subsection{Employed models}
\section{Evaluation}
This section comprehensively evaluates our models and their performance on the dataset and validating sets. Later, goes on to determine the model which best classified our selected websites based on network packet data.
\subsection{Dataset}
\subsection{Model Evaluation}
\subsection{Model Comparison and Evaluation Results}

>>>>

\subsection{Capturing Data}
\subsubsection{Wireshark}
\subsubsection{Data Collection}

\subsection{Data Preparation and Processing}

\subsubsection{Feature Selection}
\subsubsection{Data Formatting}

\subsection{Employed models}
\subsubsection{Logistic Regression (Baseline)}

\subsubsection{K-Nearest Neighbors}

\subsubsection{Random Forest}

\subsubsection{Neural Network}
\section{Evaluation}
This section comprehensively evaluates our models and their performance on the dataset and validating sets. Later, goes on to determine the model which best classified our selected websites based on network packet data.
\subsection{Dataset}
\subsection{Evaluation Metrics}
Accuracy and Macro F1 score are the primary metrics used to evaluate each model. These metrics are applicable to all models and allow for
a direct comparison for each of their performances. Two other metrics: precision and recall, help to provide a more detailed understanding of the model's performance on a class-to-class basis.
\subsection{Model Comparison and Evaluation Results}
